### 2020-03-05 main_text/main_text.tex
Edits to expt details + author list & minor polish
More edits & polish on materials & methods

	When all genes of the \emph{xapABR} circuit are removed, the
	xanthosine response of our reporter construct disappears (see
	Fig~\subref{fig1:data}{A}, left panel).
	This is the result of removing the transcription factor XapR that is
	induced by xanthosine. When only the genes \emph{xapAB} are removed
	but \emph{xapR} is kept, a response to the xanthosine concentration
	is regained but it is no longer switch-like (see
	Fig~\subref{fig1:data}{A}, middle panel). Instead, the distribution remains
	unimodal and simply shifts to higher expression as the xanthosine
	concentration is increased. As we will see later on, this is because
	the circuit now lacks the positive feedback loop due to the
	xanthosine membrane transporter XapB.

	As mentioned in
	the introduction, there are two binding sites for XapR on the
	\emph{xapAB} promoter: one directly at the polymerase binding site
	and one further upstream.
	Working in the \textDelta\emph{xapAB} background,
	we measured the expression level of our reporter when driven by two
	constructs: the wild-type \emph{xapAB} promoter
	(Fig~\subref{fig1:data}{B}, left panel), and the \emph{xapAB}
	promoter with the upstream binding site removed
	(Fig~\subref{fig1:data}{B}, right panel).
	Clearly, removing one XapR binding site dramatically reduced the
	responsiveness of the promoter to xanthosine (though not apparent
	from Fig~\subref{fig1:data}{B}, this response remains detectable
	in other measurements covering a smaller dynamic range).

@@

	\subsection*{Materials and Methods}
	\paragraph*{Bacterial Strains.} Strains used in this work
	derive from {\it E. coli} K12 MG1655 with the {\it lac} operon
	removed and were constructed similarly to those used in~\cite{RazoMejia2018, Belliveau2019}. $\Delta{xapAB}$ and
	$\Delta{xapABR}$ knockouts were generated using the approach of
	Datsenko and Wanner~\cite{Datsenko2000}. For the fluorescent
	reporter constructs the {\it xapAB} promoter region, with one or
	both XapR binding sites, were extracted from {\it E. coli} K12
	MG1655 by PCR. These were cloned into the YFP-expressing reporter
	plasmid pZS25, containing kanamycin resistance, and integrated at
	the {\it galK} locus using $\lambda$ Red recombineering~\cite{Sharan2009}.

	\paragraph*{Flow Cytometry Measurements.}
	Experimental measurements in Fig. 2B of the main text were obtained
	via flow cytometry and were performed in a similar manner as
	described in~\cite{RazoMejia2018}. Briefly, wild-type,
	$\Delta{xapABR}$, and $\Delta{xapAB}$ were grown to saturation in
	rich LB Miller (BD Medical) medium and were diluted 1:1000 into M9
	minimal medium supplemented with 0.5\% (w/v) glucose and the
	appropriate concentration of xanthosine. For measurements of the
	$\Delta{xapAB}$ strain, chloramphenicol was also added to the growth
	medium to ensure stability of the pZ3PN25-tetR plasmid along with 10
	ng /mL of anhydro-tetracycline to maximize expression of
	xapR-mCherry. Cultures were allowed to grow at $37\unit{^\circ C}$ for six
	to eight hours to an OD$_{600\unit{nm}}$ of $\approx 0.3$. At this point,
	the cultures were diluted 1:10 into M9 + 0.5\% glucose and were
	immediately analyzed via a MacsQuant VYB Flow Cytometery
	(MiltenyiBiotec). Measurement files were exported to CSV file
	formats and analyzed as previously described
	in~\cite{RazoMejia2018}.

@@

@@

>>>>

	When all genes of the \emph{xapABR} circuit are removed, the
	xanthosine response of our reporter construct disappears (see
	Fig~\subref{fig1:data}{A}, middle panel).
	This is the result of removing the transcription factor XapR that is
	induced by xanthosine. When only the genes \emph{xapAB} are removed
	but \emph{xapR} is kept, a response to the xanthosine concentration
	is regained but it is no longer switch-like (see
	Fig~\subref{fig1:data}{A}, right panel). Instead, the distribution remains
	unimodal and simply shifts to higher expression as the xanthosine
	concentration is increased. As we will see later on, this is because
	the circuit now lacks the positive feedback loop due to the
	xanthosine membrane transporter XapB.

	As mentioned in
	the introduction, there are two binding sites for XapR on the
	\emph{xapAB} promoter: one partially overlapping the polymerase -35 site
	and one further upstream.
	Working in the \textDelta\emph{xapAB} background,
	we measured the expression level of our reporter when driven by two
	constructs: the wild-type \emph{xapAB} promoter
	(Fig~\subref{fig1:data}{B}, left panel), and the \emph{xapAB}
	promoter with the upstream binding site removed
	(Fig~\subref{fig1:data}{B}, right panel).
	Clearly, removing one XapR binding site dramatically reduced the
	responsiveness of the promoter to xanthosine (though not apparent
	from Fig~\subref{fig1:data}{B}, this response remains detectable
	in other measurements covering a smaller dynamic range).

@@

	\subsection*{Materials and Methods}
	\paragraph*{Bacterial Strains.} Strains used in this work
	derive from {\it E. coli} K12 MG1655 with the {\it lac} operon
	removed and were constructed similarly to those used in~\cite{RazoMejia2018, Belliveau2019}. 
	The $\Delta{xapABR}$ knockout was generated using the approach of
	Datsenko and Wanner~\cite{Datsenko2000}. For the fluorescent
	reporter constructs the {\it xapAB} promoter region, with one or
	both XapR binding sites, were extracted from {\it E. coli} K12
	MG1655 by PCR. These were cloned into the YFP-expressing reporter
	plasmid pZS25~\cite{Lutz1997},
	containing kanamycin resistance, and integrated at
	the {\it galK} locus using $\lambda$ Red recombineering~\cite{Sharan2009}.
	A xapR-mCherry fusion was constructed in a pZS31 plasmid and was integrated
	into the \textit{ybcN} locus, also using $\lambda$ Red recombineering.
	Expression of the xapR-mCherry fusion was regulated by TetR expressed
	extrachromosomally from a pZS3-PN25 plasmid.
	Expression of the xapR-mCherry fusion was induced by the addition of
	10~ng/mL anhydro-tetracycline.
	A similar expression system was used in~\cite{Brewster2014}
	More details can be found in~\nameref{S1_Text}.

	\paragraph*{Flow Cytometry Measurements.}
	Experimental measurements in Fig. 2 were obtained
	via flow cytometry and were performed in a similar manner as
	described in~\cite{RazoMejia2018}. Briefly, wild-type,
	$\Delta{xapABR}$, and $\Delta{xapAB}$ were grown to saturation in
	rich LB Miller (BD Medical) medium and were diluted 1:1000 into M9
	minimal medium supplemented with 0.5\% (w/v) glucose and the
	appropriate concentration of xanthosine.
	Cultures were allowed to grow at $37\unit{^\circ C}$ for six
	to eight hours to an OD$_{600\unit{nm}}$ of $\approx 0.3$. At this point,
	the cultures were diluted 1:10 into M9 + 0.5\% glucose and were
	immediately analyzed via a MacsQuant VYB Flow Cytometery
	(MiltenyiBiotec). Measurement files were exported to CSV file
	formats and analyzed as previously described
	in~\cite{RazoMejia2018}.

@@

		\bibitem{Lutz1997}
		Lutz R, and Bujard, H
		\newblock Independent and Tight Regulation of Transcriptional Units in \textit{Escherichia Coli} Via the {{LacR}}/{{O}}, the {{TetR}}/{{O}} and {{AraC}}/{{I1}}-{{I2}} Regulatory Elements.
		\newblock Nucleic Acids Research, 1997;25(6), 1203--1210.
		\newblock doi:{10.1093/nar/25.6.1203}

@@

		\bibitem{Brewster2014}
		Jones, DL, Brewster, RC, Phillips, R
		\newblock Promoter architecture dictates cell-to-cell variability in gene expression.
		\newblock Science, 2014;346(6216), 1533--1536.
		\newblock doi:{10.1126/science.1255301}

### 2020-03-05 s1_text/s1_text.tex
More edits & polish on materials & methods

\paragraph{Construction of $\bm{\Delta{xapAB}}$ strain.}
Further experiments are underway in which precise control of the xapR copy number are needed and the preliminary data from these experiments are shown in the middle panel of Fig. 2A of the main text. This strain was constructed by creating a XapR-mCherry fusion protein expressed from a tetR regulated promoter. This fusion construct was integrated into the ycbN locus of the $\Delta{xapABR}$ strain making an effective $\Delta{xapAB}$ strain. A pZS3-PN25-TetR expression plasmid was also inserted into this genetic background which permits titratable control over the xapR-mCherry copy number. For the data presented in this work, expression was maximized using $10 \unit{ng/mL}$ of the tetR inducer anhydro-tetracycline. Further information of a similar construct (LacI-mCherry) can be found in~\cite{Brewster2014} and~\cite{Chure2019}.

>>>>

\paragraph{Construction of $\bm{\Delta{xapAB}}$ strain.}
Further experiments are underway in which precise control of the xapR
copy number are needed and the preliminary data from these experiments
are shown in the right panel of Fig. 2A of the main text. This strain
was constructed by creating a XapR-mCherry fusion protein expressed from
a tetR regulated promoter. This fusion construct was integrated into the
ycbN locus of the $\Delta{xapABR}$ strain making an effective
$\Delta{xapAB}$ strain. A pZS3-PN25-TetR expression plasmid was also
inserted into this genetic background which permits titratable control
over the xapR-mCherry copy number. For the data presented in this work,
expression was maximized using $10 \unit{ng/mL}$ of the TetR inducer
anhydro-tetracycline. Further information of a similar construct
(LacI-mCherry) can be found in~\cite{Brewster2014} and~\cite{Chure2019}.
